Title here

### 2020-03-26 tex/ms.tex
tmp

>>>>

\section{Integration}

Define the pairwise difference operator
%
\begin{align}
    \label{eq:pairdiff}
    \Delta \bvec{v} \equiv \sum_{i=0}^{2N} (-1)^{i + 1} v_i
\end{align}
%
which sums the difference of successive pairs of values in 
an array $\bvec{v} = \{ v_0, v_1, v_2, v_3, {\cdot\cdot\cdot}, v_{2N}\}$.

\newcommand{\kap}{\boldsymbol{\kappa}}
\newcommand{\kmt}{k^{-2}}

\subsection{The integral $\mathcal{J}$}
%
\begin{align}
    \label{eq:J}
    \mathcal{J}_v(k, \kap) = 
        \int_{\frac{\kappa_i}{2}}^{\frac{\kappa_{i+1}}{2}}
        \sin^{2v}\varphi
        \left(1 - \kmt\sin^2\varphi\right)^\frac{3}{2} 
        \mathrm{d}\varphi
\end{align}
%
Given the lower boundary condition
%
\begin{proof}{J0}
    \label{eq:J0}
    \mathcal{J}_0(k, \kap) &= 
        \frac{1}{3} \bigg(
            2 (2 - \kmt) \Delta \mathbf{E}(k, \kap) + 
            (\kmt - 1) \Delta \mathbf{F}(k, \kap) + 
            \kmt \Delta \mathbf{z}(k, \kap)
        \bigg)
%
    \nonumber \\
%
    \mathbf{z}(k, \boldsymbol{\kappa}) &= 
        \sin\left(\frac{\kap}{2}\right) 
        \cos\left(\frac{\kap}{2}\right) 
        \sqrt{1 - \kmt \sin^2\left(\frac{\kap}{2}\right)}
\end{proof}
%
and an upper boundary condition $\mathcal{J}_N$ 
(computed by numerical integration of Equation~\ref{eq:J}),
the values of all intermediate $J_v$ can be obtained by solving the following
tridiagonal problem:
%
\begin{proof}{Jtri}
    \label{eq:Jtri}
    \begin{pmatrix}
        a_0   & 1     &       &       &       &       \\
        b_1   & a_1   & 1     &       &       &       \\
            & b_2   & a_2   & 1     &       &       \\
            &       & b_0   & a_3   & 1     &       \\
            &       &       & \ddots& \ddots&\ddots \\
            &       &       &       & b_N   & a_N   
    \end{pmatrix}
    \begin{pmatrix}
        \mathcal{J}_1 \\
        \mathcal{J}_2 \\
        \mathcal{J}_3 \\
        \mathcal{J}_4 \\
        \cdot\cdot\cdot \\
        \mathcal{J}_{N-1}
    \end{pmatrix}
    =
    \begin{pmatrix}
        c_0 - b_0 \mathcal{J}_0 \\
        c_1 \\
        c_2 \\
        c_3 \\
        \cdot\cdot\cdot \\
        c_N - \mathcal{J}_N
    \end{pmatrix}
\end{proof}
%
where the recursion coefficients are given by
%
\begin{proof}{Jtri}
    \label{eq:Jtri_coeffs}
    a_v(k) &= -2\frac{(v + 1) + (v - 1) k^2}{2v + 3} \nonumber \\
    b_v(k) &= \frac{(2v - 3) k^2}{2v + 3} \nonumber \\
    c_v(k, \kap) &= \frac{\Delta \mathbf{q_v}(k, \kap)}{2v + 3} \nonumber \\
    \mathbf{q_v}(k, \kap) &= 
        k^2 
        \sin^{2v + 1}\left(\frac{\kap}{2}\right) 
        \cos\left(\frac{\kap}{2}\right) 
        \bigg(1 - \kmt \sin^2\left(\frac{\kap}{2}\right)\bigg)^\frac{5}{2}
\end{proof}
